Approximate Bayesian Computation in Large Scale Structure: constraining the galaxy-halo connection

### 2017-03-08 ccppabc/text/response.md

Dear Editor,

This was a very constructive report and we have made revision to the paper
accordingly. We think the comments have led to improvement in quality of the paper.

ChangHooh Hahn & Mohammadjavad Vakili (on behalf of the authors):

-----
We are grateful to the constructive and helpful comments of the 
anonymous referee on our manuscript. They have led to improvements in the paper.  
In what follows, the referee comments are indented and our responses are not indented:
-----

> a deeper discussion on why the ABC approach should be preferred in this particular context 
(one or two phrases on this should be included in the abstract).

>in section 3.4 it is said: "Furthermore, the Gaussian-likelihood approach relies on constructing an accurate covariance
matrix estimate that captures the sample variance of the data. While we are able to
do this accurately within the scope of the HOD framework, for more general LSS parameter
inference situations, it is both labor and computationally expensive and dependent on the
accuracy of simulated mock catalogs, which are known to be unreliable on small scales (see
Heitmann et al. 2008; Chuang et al. 2015 and references therein). Since ABC-PMC utilizes
a forward model to account for sample variance, it does not depend on a covariance matrix
estimate; hence it does not face these problems."
this might lead to confusion. Do the authors believe that ABC presents no advantage  
in the specific case studied in this paper?

> if the Gaussian hypothesis underlying the standard approach are so unrealistic 
as stated in the text, why results are still consistent with the ABC ones? 
how likely it is that we will face a real data scenario which might lead to significantly different results?

> is it possible to simulate an extreme data situation where the results from 
the standard analysis are not consistent with the ABC ones? if so,  how realistic it is?

> what caveats one would face in trying to  apply this kind of analysis in real data? 
How can they affect the final results and how can they be circumvented?

### 2017-03-08 ccppabc/text/revision/main.tex
some text to address issue 3 (referee's extreme data comment)
section 3.4

%%%
{\bf \color{dred} 
Overall, the constraints from ABC-PMC are consistent with those from 
the Gaussian pseudo-likelihood MCMC method; however, using ABC-PMC has a number of 
advantages. ABC-PMC utilizes a forward generative model. Our forward generative model, 
for instance, accounts for sample variance. Forward generative models also have the 
advantage that they can account for sources of systematic uncertainties that affect 
observational data.
}
%%%

@@

%%%
{\bf \color{darkgreen} 
CHH: @MJV I'm not a big fan of this entire paragraph. The accuracy of the covariance
matrix depends on the accuracy of the mock catalogs (a.k.a. the forward model). While it's definitely 
true that on small scales they break down, forward models in ABC suffers from the same issues.
} 
%%%
Furthermore, the Gaussian-likelihood  approach relies on constructing an accurate covariance matrix
estimate that captures the sample variance of the data. While we are able to do this accurately 
within the scope of the HOD framework, for more general LSS parameter inference situations, it 
is both labor and computationally expensive and dependent on the accuracy of simulated mock catalogs,
which are known to be unreliable on small scales (see \citealt{cosmiccode,nifty} and references therein). 
Since ABC-PMC utilizes a forward model to account for sample variance, it does not depend on a 
covariance matrix estimate; hence it does not face these problems.

>>>>

%%%
{\bf \color{dred} 
Overall, the constraints from ABC-PMC are consistent with those from 
the Gaussian pseudo-likelihood MCMC method; however, using ABC-PMC has a number of 
advantages. ABC-PMC utilizes a forward generative model. Our forward generative model, 
for instance, accounts for sample variance. Forward generative models also have the 
advantage that they can account for sources of systematic uncertainties that affect 
observational data.
}

{\bf \color{dred}
It is possible to consider a scenario in which the results from the standard analysis are inconsistent with the results from the ABC. Let us consider a dataset---from a galaxy survey---consisting of objects with different data qualities, signal-to-noise ratios, and systematic effects. This could be a catalog of galaxies which is incomplete beyond a certain luminosity or redshift. Another example could be a catalog with a singal-to-noise ratio cut. 
}

{\bf \color{dred}
In standard likelihood analyses, these selection effects, if not accounted for, can lead to biases in the inferred parameters of interest. Hierarchical models can modify the likelihood functions through by taking into account the selection effects. Alternatively, one could alleviate this issue by employing ABC equipped with a generative forward model of the data that incorporates signal-to-noise ratio cuts, incompleteness, etc.
}{\bf \color{darkgreen}
MJV: @CHH Can you read the two paragraphs above and see if they address referee's concern about the extreme data situation that could lead to discrepancy ?
}
%%%

@@

%%%
{\bf \color{darkgreen}
MJV: @CHH I think this paragraph is misleading since both ABC and Gaussian likelihood covariances suffer from inaccuracy of the simulations. I say we remove this paragraph entirely. It does not add any clarify anything. It just causes confusion!
}
{\bf \color{darkgreen} 
CHH: @MJV I'm not a big fan of this entire paragraph. The accuracy of the covariance
matrix depends on the accuracy of the mock catalogs (a.k.a. the forward model). While it's definitely 
true that on small scales they break down, forward models in ABC suffers from the same issues.
} 
%%%
Furthermore, the Gaussian-likelihood  approach relies on constructing an accurate covariance matrix
estimate that captures the sample variance of the data. While we are able to do this accurately 
within the scope of the HOD framework, for more general LSS parameter inference situations, it 
is both labor and computationally expensive and dependent on the accuracy of simulated mock catalogs,
which are known to be unreliable on small scales (see \citealt{cosmiccode,nifty} and references therein). 
Since ABC-PMC utilizes a forward model to account for sample variance, it does not depend on a 
covariance matrix estimate; hence it does not face these problems.
